<small> Supplementary materials for the main submission entitled - <br><br> Detecting distributional differences between temporal granularities for exploratory time series analysis

### 2022-02-28 paper/paper-supplementary.Rmd
supplementary paper update

bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% 
  mutate(estimate = round(estimate, 2),
         std.error = round(std.error, 3),
         statistic = round(statistic, 2),
         p.value = round(p.value, 2)) %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for $m=1$.")

>>>>

bind_cols(distribution = "N(0, 1)", broom::tidy(glm_fit_onegran)) %>% 
  mutate(estimate = round(estimate, 2),
         std.error = round(std.error, 3),
         statistic = round(statistic, 2),
         #p.value = round(p.value, 2)
         p.value = "<.001") %>% kable(caption = "Results of generalised linear model to capture the relationship between $\\wpdsub{raw}$ and number of comparisons for $m=1$.")
